### 2022-05-18 README.Rmd
Added R CMD CHECK badge

`r badge_custom(x = "arXiv", y = "abs/2106.10539", color = "yellow", url = "https://arxiv.org/abs/2106.10539")` 
`r badge_cran_release("fasano.franceschini.test", "orange")`
`r badge_devel("nesscoder/fasano.franceschini.test", "blue")` 
`r badge_cran_download("fasano.franceschini.test", "grand-total", "green")`
[![R-CMD-check](https://github.com/cpuritz/fftest/workflows/R-CMD-check/badge.svg)](https://github.com/cpuritz/fftest/actions)
<!-- badges: end -->

>>>>

`r badge_custom(x = "arXiv", y = "abs/2106.10539", color = "yellow", url = "https://arxiv.org/abs/2106.10539")` 
`r badge_cran_release("fasano.franceschini.test", "orange")`
`r badge_devel("nesscoder/fasano.franceschini.test", "blue")` 
`r badge_cran_download("fasano.franceschini.test", "grand-total", "green")`
`r badge_github_actions("nesscoder/fasano.franceschini.test")`
<!-- badges: end -->
